\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 18\\
Kelvin & 17\\
Luna & 17\\
Mazen & 18\\
Rawan & 17\\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: Pavel Volgarev }

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Kelvin & 2\\
Luna & 2\\
Mazen & 2\\
Rawan & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Kelvin & 1\\
Luna & 2\\
Mazen & 2\\
Rawan & 1\\
\bottomrule
\end{tabular}
\end{table}


\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: }

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Kelvin & 1\\
Luna & 1\\
Mazen & 1\\
Rawan & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & Num & 100\% \\
Kelvin & 10 & \% \\
Luna & 34 & \% \\
Mazen & 17 & \% \\
Rawan & 30 & \% \\
\bottomrule
\end{tabular}
\end{table}

Although commit counts differ among team members, all members contributed equally to the project. The variation is due to differences in how work was structured—some features were completed in fewer, larger commits, while others were developed through many smaller commits.
\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Luna   & 13 & 12 \\
Mazen  & 11 & 5  \\
Kelvin & 7  & 6  \\
Rawan  & 12 & 6  \\
\bottomrule
\end{tabular}
\caption{Issue tracker contributions by team member}
\end{table}

While issue tracking was used to organize much of the work, not all contributions were directly tied to issues. Some smaller tasks, quick fixes, and collaborative efforts were completed without creating or assigning issues for efficiency. Therefore, issue counts may not fully represent each team member’s overall contribution.
\section{Team Charter Trigger Items}

There are currently no new team charter trigger items. The team has been contributing effectively, with all members actively participating in both commits and issue management. Overall, collaboration has been strong, and responsibilities have been shared fairly, with each member supporting the completion of tasks and milestones on time.

\section{Additional Productivity Metrics}

No other productivity metrics were tracked during this reporting period.

\end{document}