\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{float}
\usepackage{booktabs}

\title{Reflection and Traceability Report on \progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This report provides a comprehensive reflection on the development and evolution of the VoiceBridge system from Revision 0 to Revision 1. The primary objective of this document is to demonstrate traceability between external feedback—received from teaching assistants, faculty advisors, and peer reviewers—and the subsequent refinements made to the system's requirements, design, and verification protocols. This Document serves as a critical assessment of the engineering learning outcomes achieved throughout the Capstone project, including design iteration, project management efficiency, and the ethical considerations of developing assistive technologies.
\section{Changes in Response to Feedback}

% \plt{Summarize the changes made over the course of the project in response to
% feedback from TAs, the instructor, teammates, other teams, the project
% supervisor (if present), and from user testers.}

% \plt{For those teams with an external supervisor, please highlight how the feedback 
% from the supervisor shaped your project.  In particular, you should highlight the 
% supervisor's response to your Rev 0 demonstration to them.}

% \plt{Version control can make the summary relatively easy, if you used issues
% and meaningful commits.  If you feedback is in an issue, and you responded in
% the issue tracker, you can point to the issue as part of explaining your
% changes.  If addressing the issue required changes to code or documentation, you
% can point to the specific commit that made the changes.  Although the links are
% helpful for the details, you should include a label for each item of feedback so
% that the reader has an idea of what each item is about without the need to click
% on everything to find out.}

% \plt{If you were not organized with your commits, traceability between feedback
% and commits will not be feasible to capture after the fact.  You will instead
% need to spend time writing down a summary of the changes made in response to
% each item of feedback.}

% \plt{You should address EVERY item of feedback.  A table or itemized list is
% recommended.  You should record every item of feedback, along with the source of
% that feedback and the change you made in response to that feedback.  The
% response can be a change to your documentation, code, or development process.
% The response can also be the reason why no changes were made in response to the
% feedback.  To make this information manageable, you will record the feedback and
% response separately for each deliverable in the sections that follow.}

% \plt{If the feedback is general or incomplete, the TA (or instructor) will not
% be able to grade your response to feedback.  In that case your grade on this
% document, and likely the Revision 1 versions of the other documents will be
% low.} 
\subsection{SRS and Hazard Analysis}

Over the course of the project, we made targeted updates to the SRS and Hazard
Analysis in response to TA feedback, advisor guidance, and internal review. The
main themes were: (i) improving requirement precision and testability, (ii)
clarifying system boundaries and privacy assumptions for a local-first assistive
tool, and (iii) strengthening safety language around command execution and user
confirmation.

\begin{itemize}

\item \textbf{Clarified system boundary and privacy assumptions}

\textbf{Source:} TA/advisor feedback during Revision 0 review and demo discussions.

\textbf{Feedback:} The boundary between what runs locally vs.\ what relies on
external components was not explicit enough, which made feasibility and privacy
risk harder to assess.

\textbf{Response:} We revised the SRS to state the local-first intent more
clearly, identify external dependencies where applicable, and tighten definitions
around what user data exists, where it can be stored, and what is not retained by
default.

\item \textbf{Improved requirement specificity and testability}

\textbf{Source:} TA feedback on requirement quality.

\textbf{Feedback:} Some requirements were too high-level or combined multiple
behaviours, reducing testability and traceability.

\textbf{Response:} We reworded several requirements to be more measurable (clear
triggers, observable outputs, and success criteria) and split bundled
requirements so each one maps cleanly to design elements and V\&V tests.

\item \textbf{Strengthened traceability between SRS/HA and the design docs}

\textbf{Source:} TA feedback emphasizing traceability, including the design
documentation review
(\href{https://github.com/speech-buddies/VoiceBridge/issues/235}{TA Review \#235}).

\textbf{Feedback:} The design documentation needed clearer, more consistent
module responsibilities and mappings, and the project artifacts needed to remain
traceable across documents.

\textbf{Response:} While \#235 primarily drove updates to the design documents,
addressing it required us to cross-check the design against the SRS and Hazard
Analysis. We verified and tightened SRS-to-module and hazard/mitigation-to-module
traceability to reduce drift and ensure that safety and privacy assumptions in
the SRS/HA were reflected in the architecture.

\item \textbf{Expanded hazards related to unintended command execution}

\textbf{Source:} TA feedback and internal risk review after implementing command
execution flows.

\textbf{Feedback:} The hazard analysis under-emphasized risks from
misrecognition, ambiguous intent, and executing harmful browser actions.

\textbf{Response:} We strengthened hazards and mitigations around incorrect
transcriptions and ambiguous commands leading to unintended actions. Mitigations
were updated to emphasize explicit confirmation for higher-risk actions, clear
user feedback during execution, and safe fallback behaviour when commands are
out-of-scope or low-confidence.

\item \textbf{Made privacy and data-retention hazards more concrete}

\textbf{Source:} TA/advisor feedback on privacy risk articulation.

\textbf{Feedback:} Privacy hazards were present but too abstract, making it
unclear what data might be logged or retained and what controls exist.

\textbf{Response:} We clarified which artifacts (e.g., transcripts, recordings,
logs, and user settings) might exist and refined mitigations to emphasize
minimizing stored sensitive data, limiting log exposure, and treating stored
artifacts as sensitive by default.

\item \textbf{Addressed accessibility-related failure modes as safety/usability risks}

\textbf{Source:} TA feedback and usability-oriented review.

\textbf{Feedback:} Since the target users include individuals with dysarthric
speech, the analysis should consider failure modes such as unclear prompts,
missing confirmations, or confusing system state.

\textbf{Response:} We added/refined hazards capturing user confusion and loss of
control due to insufficient feedback, and we connected mitigations to clearer
state indications and consistent confirm/cancel interactions.

\end{itemize}

\subsection{Design and Design Documentation}

Most of our feedback-driven changes were in the design documentation, where we
focused on improving clarity, consistency, and alignment with the implemented
system.

\begin{itemize}

\item \textbf{Improved module boundaries and responsibility descriptions}

\textbf{Source:} TA feedback on ambiguity/overlap between components.

\textbf{Feedback:} Some responsibilities were described in overlapping terms
(e.g., session flow vs.\ command interpretation vs.\ browser execution), making
it hard to understand component ownership.

\textbf{Response:} We revised the Module Guide's module descriptions to better
separate responsibilities (UI/feedback vs.\ transcription vs.\ command synthesis
vs.\ execution/orchestration vs.\ storage/security). This made the architecture
easier to understand and reduced ambiguity for implementation and testing.

\item \textbf{Updated documentation to match the final implementation}

\textbf{Source:} TA/advisor feedback plus internal consistency checks.

\textbf{Feedback:} Some design text reflected earlier architecture drafts rather
than the final code structure, creating ``documentation drift.''

\textbf{Response:} We updated module descriptions and terminology so they
accurately reflect the final architecture and how the system is implemented
(including details of the audio capture flow and the model tuning workflow).
This improved the MG's usefulness as a maintenance reference.

\item \textbf{Strengthened traceability matrices and requirement coverage}

\textbf{Source:} TA feedback emphasizing traceability and completeness.

\textbf{Feedback:} The design needed clearer evidence that requirements
(functional, usability, performance, security, etc.) were mapped to concrete
parts of the system.

\textbf{Response:} We revised and validated the traceability matrices so each
requirement category maps to the relevant modules, and we checked for
gaps/duplicates. This also helped ensure the V\&V work could be planned directly
against the design.

\item \textbf{Clarified inter-module communication and error handling}

\textbf{Source:} Advisor/TA feedback requesting clearer interaction details.

\textbf{Feedback:} The documents needed clearer description of how modules
exchange information and how errors propagate to user-facing feedback.

\textbf{Response:} We expanded the design documentation to describe the
message/data flow at a high level (what data types are passed, where session
state is tracked, and how failures are turned into user-facing feedback and
logs). This made the design more actionable and easier to verify.

\item \textbf{Refined UI and accessibility documentation based on feedback}

\textbf{Source:} TA feedback and informal user-focused review.

\textbf{Feedback:} The UI story needed clearer user-state feedback (listening,
processing, confirm/cancel) and accessibility justification.

\textbf{Response:} We improved UI-related sections and figures/descriptions to
emphasize predictable state transitions, clear confirmations, and accessible
feedback. These changes were motivated by the needs of users with dysarthric
speech, where system confidence and clarity directly affect usability.

\end{itemize}

\subsection{VnV Plan and Report}

The VnV Plan and associated report were revised to incorporate feedback from peer reviews and formal TA review. The changes focused on improving traceability, making nonfunctional tests more specific, clarifying the scope of extras, and refining document language for readability.

\begin{table}[H]
\caption{VnV Report}
\begin{tabularx}{\textwidth}{p{4cm}X}
  \toprule
  \textbf{Issue} & \textbf{Response and Change} \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/91}{Peer Review \#91} & Expanded the VnV Plan traceability matrix so every nonfunctional test case is explicitly linked to the corresponding SRS nonfunctional requirement. This made the relationship between look-and-feel tests, usability/humanity tests, and the SRS clear. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/92}{Peer Review \#92} & Proofread and corrected grammar and structure throughout the VnV documents. We simplified long sentences, improved section flow, and made the VnV Plan easier to follow. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/93}{Peer Review \#93} & Added concrete test details for nonfunctional cases. In particular, the ASR latency benchmark now includes the source and selection method for audio samples, the measurement procedure, and the expected results. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/94}{Peer Review \#94} & Clarified extras feasibility and marked as wont fix per TA/instructor instructions. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/95}{Peer Review \#95} & Added detailed nondynamic testing plans, including roles for code inspections, document reviews, and static analysis in Sections 3.6 and 3.7. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/96}{Peer Review \#96} & Expanded Section 2.2 with testable objectives linked to critical qualities. Revised Section 2.3 to identify extra verification activities and their feasibility. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/116}{TA Review \#116} & Addressed TA comments on the VnV Plan and report by refining the document structure, improving traceability, and tightening wording to better align with the review feedback. \\
  \bottomrule
\end{tabularx}
\end{table}



The VnV Report was revised to incorporate feedback from peer reviews. The changes focused on improving traceability and providing explanations for test results.

\begin{table}[H]
\caption{VnV Report}
\begin{tabularx}{\textwidth}{p{4cm}X}
  \toprule
  \textbf{Issue} & \textbf{Response and Change} \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/286}{Peer Review \#286} & Clarified changes made due to testing by directly linking them to specific test results and outcomes. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/287}{Peer Review \#287} & Updated test results to show actual quantitative data and align with VnV Plan pass criteria. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/288}{Peer Review \#288} & Added missing test cases (test-LF-1, test-LF-2, test-OER-1, test-OER-2) to the VnV Report. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/289}{Peer Review \#289} & Added test FR6 to the VnV Plan to maintain traceability between the plan and report documents. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/290}{Peer Review \#290} & Explained the deferral of test-PF-3 as a stretch goal and updated the VnV Plan accordingly. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/291}{Peer Review \#291} & Provided explanation for the failing result of test-PF-1, including next steps to resolve the issue and clarify the non-functional requirement. \\
  \midrule
  \href{https://github.com/speech-buddies/VoiceBridge/issues/320}{TA Review \#320} & Addressed TA comments on the VnV Report by refining structure, results presentation, and alignment with the VnV Plan. \\
  \bottomrule
\end{tabularx}
\end{table}

\section{Extras}

% \plt{Summarize the extras that were tackled by this project.  Extras
% can include usability testing, code walkthroughs, user documentation, formal
% proof, GenderMag personas, Design Thinking, etc.  Extras should have already
% been approved by the course instructor as included in your problem statement.}
Our team completed the two following extras:

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{l p{4.5cm} X}
\hline
\textbf{Document} & \textbf{Methodology} & \textbf{Key Focus Area} \\ \hline
\textbf{Literature Review} & Semi-systematic synthesis of recent ASR research, technical reports, and working notes. & Evaluation of fine-tuning strategies, parameter-efficient methods (LoRA), and specialized preprocessing for dysarthric speech. \\
\textbf{ML Report} & Technical implementation and parameter-efficient fine-tuning (PEFT) using Whisper-small. & On-device adaptation, local privacy-preserving workflows, and mitigating catastrophic forgetting via replay buffers. \\ \hline
\end{tabularx}
\caption{Summary of VoiceBridge Research and Technical Documentation}
\label{tab:doc_summary}
\end{table}

\section{Design Iteration (LO11 (PrototypeIterate))}

% \plt{Explain how you arrived at your final design and implementation.  How did
% the design evolve from the first version to the final version?} 

% \plt{Don't just say what you changed, say why you changed it.  The needs of the
% client should be part of the explanation.  For example, if you made changes in
% response to usability testing, explain what the testing found and what changes
% it led to.}
\subsection{Audio Capture Modules}
A key iteration in our system design was consolidating the modules related to audio capture, including the former MicrophoneManager, VADCapture, etc. into one master module. The reason for this is that our team came across pre-existing open source solutions in the form of python packages that could simplify our design. The packages were the following:

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{5cm}p{6cm}}
\hline
\textbf{Library} & \textbf{Primary Function} & \textbf{Key Features} \\ \hline
\texttt{sounddevice} & Real-time audio I/O and hardware interfacing. & Provides bindings for the PortAudio library; handles multi-channel recording, low-latency streaming, and device selection. \\
\texttt{webrtcvad} & Voice Activity Detection (VAD). & Specifically designed to distinguish between human speech and background noise; uses the high-performance WebRTC VAD engine. \\ \hline
\end{tabular}
\caption{Core Audio Processing Libraries for VoiceBridge}
\label{tab:audio_libraries}
\end{table}

Given these two libraries covered microphone/audio device management as well as VAD filtering, we were able to depend on them entirely rather than creating our own modules. Thus, we were able to create a single consolidated class for collecting audio data, simplifying our design and process.

\subsection{Shortcut Manager Iteration}

One important design iteration in VoiceBridge was the development of the
\texttt{ShortcutManager}. In the earlier versions of the system, commands were
handled one at a time with no persistent way to record, save, and replay common
action sequences. While this was enough to demonstrate basic browser control, it
did not match the client need for efficiency and accessibility in repeated
everyday tasks. For a user with impaired speech, repeatedly issuing the same
sequence of voice commands can increase fatigue and reduce the overall usability
of the system. Because of this, we introduced shortcuts as a way to reduce the
number of spoken interactions required for frequent tasks.

Our first idea was relatively simple: store a shortcut as a sequence of recorded
commands and replay them later. However, once we integrated this into the live
system, we found that shortcut behavior could conflict with the runtime state
machine. For example, the user could try to begin a shortcut recording while the
system was still processing another command, or multiple parts of the backend
could attempt to modify shortcut state at the same time. This was especially
important because VoiceBridge is a real-time system with asynchronous events,
including speech capture, transcription, intent resolution, and browser
execution. As a result, we revised the design so that shortcut recording became
an explicitly managed subsystem rather than just an added list of commands.

The final design introduced a dedicated \texttt{ShortcutManager} module with a
clear internal state, persistent storage, and locking for safe concurrent
access. Instead of scattering shortcut logic across the codebase, the manager
became responsible for starting and stopping recordings, storing recorded
commands, validating shortcut names, and loading/saving shortcuts from disk.
This design was chosen to improve maintainability and prevent race conditions in
cases where multiple backend events happen close together. The use of a lock was
an important iteration because testing showed that shortcut actions could overlap
with other command-processing flows in unpredictable ways if the state was not
protected.

We also changed how shortcuts were represented. In earlier thinking, shortcuts
were treated mainly as temporary in-memory recordings for the active session.
This was limiting, because a user would lose their shortcuts between runs of the
application. Since one of the client goals was to make the system practical for
daily use, we moved to persistent storage using a local JSON-based approach.
This allowed shortcuts to survive application restarts and made the feature more
realistic as an assistive tool rather than just a demo feature. The trade-off
was that we now needed validation and structured file handling, but this was
worth it because it supported a more reliable user experience.

Another design change was motivated by usability. Initially, shortcut support was
focused only on storing the raw sequence of actions. As the design matured, we
recognized that the feature also needed clear start/stop control and user
feedback so that recording would feel predictable. Without this, a user could be
unsure whether the system was actively recording commands into a shortcut or just
executing them normally. This was especially important given our client focus on
accessibility and confidence in system behavior. We therefore refined the design
so that shortcut recording had explicit transitions, clear prompts, and tighter
integration with the system state flow.

Overall, the \texttt{ShortcutManager} evolved from a simple convenience idea
into a more structured subsystem designed around accessibility, predictability,
and safe execution. The main reason for these changes was not just technical
cleanup, but the need to better support users who benefit from reducing repeated
speech effort while still being able to trust what the system is doing.

\section{Design Decisions (LO12)}

% \plt{Reflect and justify your design decisions.  How did limitations,
%  assumptions, and constraints influence your decisions?  Discuss each of these
%  separately.}

\subsection{Iterative Model Improvements}
A key feature of VoiceBridge was developed after our Rev0 version, that being the gradual model customization and improvements through on device training. This feature introduced a set of novel challenges for our project.
\subsubsection{Privacy-Preserving Local Adaptation}
The primary challenge was leveraging user-specific data while maintaining strict privacy standards. To resolve this, we adopted an \textbf{on-device processing architecture}. No raw audio recordings or transcripts are transmitted to external servers; instead, all fine-tuning and inference tasks are executed locally on the user's hardware.

\subsubsection{Computational Efficiency on Consumer Hardware}
While the chosen base model is relatively compact, executing machine learning training remains resource-intensive for standard consumer-grade CPUs. We addressed this through a three-fold optimization strategy:
\begin{itemize}
    \item \textbf{Low-Rank Adaptation (LoRA):} As previously detailed, LoRA is utilized to drastically reduce the number of trainable parameters.
    \item \textbf{Targeted Decoupling:} Training is restricted exclusively to the \textbf{decoder} portion of the Whisper architecture—where language and vocabulary adaptation occur—while the \textbf{encoder} remains frozen. This focuses the computational effort on user-specific linguistic patterns while preserving general acoustic features.
    \item \textbf{Incremental Batching:} Rather than retraining on the entire accumulated dataset, the system performs small, incremental updates. Training is triggered after collecting several hundred new samples and is designed to complete within a short window (typically under 20 minutes), allowing for gradual improvement without intensive resource sessions.
\end{itemize}

\subsubsection{System Responsiveness and Latency}
Executing local retraining on consumer hardware poses a risk of system instability or "bogging down" the primary interface. To maintain a fluid user experience, the application isolates the training pipeline within a **background thread**. This asynchronous execution ensures that the main application logic and user interface remain responsive and uninterupted during the adaptation process.

\subsubsection{Mitigating Catastrophic Forgetting}
A final challenge involves maintaining the model’s general accuracy during iterative updates. In machine learning, repeated training on limited new data can lead to \textbf{Catastrophic Forgetting}, where the model loses previously acquired patterns. To mitigate this, we implemented a \textbf{replay buffer system}. A subset of historically relevant samples is retained and interleaved with new data during each training cycle. This ensures the model effectively incorporates new user-specific patterns while preserving its foundational knowledge and overall transcription stability.

\section{Economic Considerations (LO23)}

% \plt{Is there a market for your product? What would be involved in marketing your 
% product? What is your estimate of the cost to produce a version that you could 
% sell?  What would you charge for your product?  How many units would you have to 
% sell to make money? If your product isn't something that would be sold, like an 
% open source project, how would you go about attracting users?  How many potential 
% users currently exist?}

Given our product is open source, there are limited economic considerations. Marketing our product would involve community outreach and promotion on public forums that can reach individuals with dysarthria. This may include getting it touch with organizations that are specialized in speech accessibility, or simply online forums like reddit. These initiatives would be done with the goal of recruiting participants and open source developers to further the research and development of the product rather than to sell it or generate profit.  

\section{Reflection on Project Management (LO24)}

\subsection{How Does Your Project Management Compare to Your Development Plan}

Our project management aligned well with our Development Plan. We maintained a
consistent meeting rhythm to coordinate priorities and remove blockers, and we
used asynchronous communication between meetings to keep work moving. We used
GitHub Issues and pull requests to plan tasks, record feedback, and track progress
across deliverables. Team roles were clear and helped us work efficiently, while
still allowing collaboration across areas when needed. We also used the
technologies we planned on using (GitHub for version control and coordination,
and LaTeX for documentation), and we kept our workflow structured around
reviewable changes and traceability.

\subsection{What Went Well?}

\begin{itemize}
  \item \textbf{Issue tracking and traceability:} Capturing peer and TA feedback
  as GitHub Issues made it easy to plan changes and clearly demonstrate
  traceability from comments to updates.
  \item \textbf{Clear ownership with collaboration:} Assigning primary owners for
  major deliverables improved consistency and helped each document progress
  steadily, while collaboration ensured quality and shared understanding.
  \item \textbf{Review and iteration:} Regular internal review cycles improved
  clarity, consistency, and alignment across the SRS/HA, design documentation,
  and V\&V artifacts.
  \item \textbf{Coordination across implementation and documentation:} Keeping
  documentation connected to the implementation helped ensure design decisions
  were well-justified and supported by the final system.
\end{itemize}

\subsection{What Went Wrong?}

\begin{itemize}
  \item \textbf{Continuous alignment effort:} Maintaining alignment between
  requirements, design, and V\&V artifacts required ongoing attention, and the
  experience reinforced the value of regularly revisiting traceability links as
  the system evolves.
  \item \textbf{Nonfunctional evaluation planning:} Defining measurable
  nonfunctional tests and presenting quantitative results clearly was a valuable
  learning area that strengthened the quality of our V\&V work.
  \item \textbf{Estimating integration work:} Coordinating integration across
  components highlighted the importance of explicitly planning interface details
  and test hooks early, which improved the final system robustness.
\end{itemize}

\subsection{What Would you Do Differently Next Time?}

\begin{itemize}
  \item \textbf{Make traceability updates routine:} Update traceability matrices
  on a regular schedule so cross-document consistency is maintained continuously.
  \item \textbf{Define acceptance criteria for issues:} Add short, explicit
  acceptance criteria to issues to keep scope clear and improve verification.
  \item \textbf{Plan earlier nonfunctional baselines:} Establish performance and
  usability baselines earlier so evaluation is repeatable and comparisons across
  iterations are straightforward.
\end{itemize}

\section{Ethics and Equity (LO18)}

Equity and universal design were central to VoiceBridge because the system is
intended to support individuals with dysarthric speech. We designed for clarity,
predictability, and user control by emphasizing clear system-state feedback
(listening, processing, executing), confirmation for higher-risk actions, and
safe handling of low-confidence or out-of-scope commands. We also treated privacy
as part of equitable design by documenting data assumptions and encouraging
local-first handling where feasible, so users can understand and trust how their
information is processed. Across the project, we aimed to reduce unnecessary
cognitive load and promote confidence by keeping interactions consistent and
transparent.

\section{Reflection on Capstone}

\subsection{Which Courses Were Relevant}

\begin{itemize}
  \item \textbf{SFWRENG 4HC3 (Human-Computer Interaction):} Informed our focus on
  usable, predictable interactions, user feedback, and accessibility-oriented
  design decisions.
  \item \textbf{SFWRENG 3A04 (Software Architecture):} Supported our approach to
  module decomposition, clear responsibility assignment, and documenting
  interfaces and system structure.
  \item \textbf{SFWRENG 4AL3 (Applied Machine Learning):} Helped us reason about
  ASR-related considerations such as evaluation, error modes, and performance
  tradeoffs in practical settings.
\end{itemize}

\subsection{Knowledge/Skills Outside of Courses}

\begin{itemize}
  \item \textbf{End-to-end ASR pipeline integration:} Building and integrating a
  real-time flow from audio capture to transcription to command execution.
  \item \textbf{Practical evaluation:} Designing repeatable procedures and
  metrics (e.g., latency and error characterization) that reflect real usage.
  \item \textbf{Privacy-aware engineering:} Translating privacy expectations into
  concrete requirements, hazards, and mitigations for an assistive tool.
  \item \textbf{Documentation and maintenance discipline:} Keeping requirements,
  design, and V\&V artifacts consistent through traceability as the project
  evolved.
  \item \textbf{Collaborative workflow:} Applying issue tracking, pull requests,
  and structured reviews to coordinate work and justify changes.
\end{itemize}

\end{document}