\begin{enumerate}
\item \textbf{What went well while writing this deliverable?}
Writing this deliverable progressed smoothly due to effective collaboration and clear communication among team members. 
The team successfully maintained consistency in formatting and terminology throughout the document, resulting in a cohesive and professional presentation.
Peer feedback helped identify and resolve ambiguities early, which enhanced the overall quality and clarity of the deliverable.

\item \textbf{What pain points did you experience during this deliverable, and how did you resolve them?}
Some challenges arose in maintaining consistent LaTeX formatting, especially with complex tables and detailed semantic descriptions.
To resolve these issues, the team adopted established LaTeX best practices and created templates to ensure uniformity. 
Additionally, scheduled review meetings allowed the team to discuss and fix formatting inconsistencies collaboratively.

\item \textbf{Which of your design decisions stemmed from speaking to your client(s) or a proxy (e.g., your peers, stakeholders, potential users)? For those that were not, why, and where did they come from?}
Many design decisions, particularly those related to user interface and accessibility, were influenced by discussions with our supervisor. 
His feedback emphasized the importance of compliance with intuitive user workflows. Decisions not directly influenced by supervisor input were grounded in recognized industry standards, prior project experience, and academic literature.

\item \textbf{While creating the design doc, what parts of your other documents (e.g., requirements, hazard analysis, etc), if any, needed to be changed, and why?}
During the design process, previous documents, such as the requirements and hazard analysis documents were reviewed, but no changes were made to them.
The design focused on clarifying module responsibilities and interface definitions, such as refining interface details to improve modularity and error handling. These efforts ensured alignment and consistency across all project documentation.

\item \textbf{What are the limitations of your solution? Put another way, given unlimited resources, what could you do to make the project better? (LO_ProbSolutions)}
The current solution has limitations regarding scalability and adaptability in diverse deployment scenarios. 
With unlimited resources, we would invest in extensive automated testing frameworks and incorporate advanced machine learning techniques for improved personalization and robustness. Additionally, comprehensive accessibility audits and user testing would be expanded to further enhance usability.

\item \textbf{Give a brief overview of other design solutions you considered. What are the benefits and tradeoffs of those other designs compared with the chosen design? From all the potential options, why did you select the documented design? (LO_Explores)}
Alternative designs considered included monolithic architectures and different modular breakdowns. Monolithic design offered simplicity but reduced maintainability and scalability. Various modular structures were explored; the chosen modular design balances separation of concerns, ease of integration, and parallel development capability. This approach was selected to optimize maintainability and accommodate future enhancements efficiently.
\end{enumerate}