\begin{enumerate}
  \item \textbf{What went well while writing this deliverable?} \\
  Organizing the SRS using the Volere template went surprisingly smoothly. Breaking down each requirement and writing clear rationales helped us think through the project in a structured way. Separating likely-to-change requirements from unlikely ones also made the document more readable and easier to navigate.

  \item \textbf{What pain points did you experience during this deliverable, and how did you resolve them?} \\
  Deciding which requirements might evolve over time versus those that would remain stable was a bit challenging. We resolved this by discussing potential future scenarios for the product and weighing Dr. Brodbeck’s expert guidance, which made our decisions much more confident.

  \item \textbf{How many of your requirements were inspired by speaking to your client(s) or their proxies?} \\
  Our requirements mostly came from our supervisor, Dr. Brodbeck, who is a linguistics expert and acts as our secondary stakeholder. We didn’t consult end-users directly, so the requirements reflect expert advice on accessibility, usability, and system functionality.

  \item \textbf{Which of the courses you have taken, or are currently taking, will help your team succeed with this project?} \\
  \begin{itemize}
    \item \textbf{SFWRENG 3RA3 – Software Requirements and Security:} Helped with writing clear Functional and Non-Functional Requirements and thinking about security, privacy, and reliability.
    \item \textbf{SFWRENG 4HC3 – Human-Computer Interfaces:} Provided a foundation for usability, stakeholder engagement, and accessibility considerations.
    \item Other courses in AI and Machine Learning are also valuable for speech recognition and natural language understanding.
  \end{itemize}

  \item \textbf{What knowledge and skills will the team need to successfully complete this project?} \\
  We need to improve on:
  \begin{itemize}
    \item Speech and linguistics for accessibility.
    \item Web development, particularly browser extensions.
    \item Machine learning for speech recognition.
    \item Accessibility standards and usability testing.
    \item Clear documentation and team coordination.
  \end{itemize}

  \item \textbf{How will each team member acquire these skills or knowledge?} \\
  \begin{itemize}
    \item \textbf{Speech and linguistics:} Weekly guidance from Dr. Brodbeck and reading related literature.
    \item \textbf{Web development/browser extensions:} Hands-on prototyping, online tutorials, and sharing coding tasks among team members.
    \item \textbf{Machine learning:} Experimenting with pre-trained speech models and following online courses.
    \item \textbf{Accessibility standards:} Reviewing WCAG guidelines and testing our prototype with assistive technologies.
  \end{itemize}
\end{enumerate}
